The Journey from Wild to Textbook Data: A Case Study from the National Longitudinal Survey of Youth

### 2021-09-14 paper/paper.Rmd

# Data Cleaning {#cleaning}

@@

```{r sample-plot, echo = FALSE, fig.cap="Getting a glimpse of the data: random sample of 36 individuals, divided into  twelve subplots. Wages are shown against year. There is a lot of variability in wages.", fig.height=4, fig.width=5}
```

@@

```{r feature-plot, fig.cap = "Several plots showing anomalies observed the input data. XX Add a couple more plots that reveal the initial problems in the data. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value. We can see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed.", fig.width=6, fig.height=4}
```

@@

>>>>

# The NLSY79 Data Cleaning {#cleaning}

@@

@@

```{r feature-plot, fig.cap = "Two plots showing the distribution of the mean hourly wage. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value. We can see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed.", fig.width=6, fig.height=4}
```

@@

```{r sample-plot, echo = FALSE, fig.cap="The mean hourly wages of some random samples are shown in twelve facets, three IDs per facet. It suggests that some IDs had a reasonably fluctuate wages.", fig.height=4, fig.width=5}
```

### 2021-09-14 paper/paper.tex

\hypertarget{cleaning}{%
\section{Data Cleaning}\label{cleaning}}

@@

\caption{Getting a glimpse of the data: random sample of 36 individuals, divided into  twelve subplots. Wages are shown against year. There is a lot of variability in wages.}\label{fig:sample-plot}
\end{figure}

@@

\caption{Several plots showing anomalies observed the input data. XX Add a couple more plots that reveal the initial problems in the data. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value. We can see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed.}\label{fig:feature-plot}
\end{figure}

@@

>>>>

\hypertarget{cleaning}{%
\section{The NLSY79 Data Cleaning}\label{cleaning}}

@@

@@

\caption{Two plots showing the distribution of the mean hourly wage. Plot A portrays the pattern of mean hourly wage of high school cohort from 1979 to 2018 of each ID in US Dollar; Plot B shows the distribution of their minimum, median, and maximum value. We can see that some IDs had an extremely high of wages and it made the distribution of the three features is extremely skewed.}\label{fig:feature-plot}
\end{figure}

@@

\caption{The mean hourly wages of some random samples are shown in twelve facets, three IDs per facet. It suggests that some IDs had a reasonably fluctuate wages.}\label{fig:sample-plot}
\end{figure}
